---
title: "Who is Faster Up and Down"
author: "Samantha Lee"
date: "Fall 2018"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
source("bootstrap.R")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
  
Are there differences between time up and down the stairs between guys and gals?
We start by loading the data into 2 data frames

```{r}
library(readr)
Sec02 <- read_csv("Class_Survey_Sec02.csv")
Sec23 <- read_csv("Class_Survey_Sec23.csv")
Sec02 <- mutate(Sec02,sect="PM")
Sec23 <- mutate(Sec23,sect="Eve")
alldat <- bind_rows(Sec02,Sec23)
```

```{r}
write.csv(x=alldat,file="alldat.csv")
```


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


Here is a box plot of the times going up and down the stairs of women and men.

```{r}
Boxplot(time_down_up~Gender, data=alldat, id=list(method="y"))
```


Looking at the graphical evidence, it appears the men went up and down the stairs about 5 seconds faster than the women.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

Here are the numerical summaries of the men and women's times.

```{r}
numSummary(alldat[,"time_down_up", drop=FALSE], 
  groups=alldat$Gender, statistics=c("mean", "sd", "IQR", 
  "quantiles"), quantiles=c(0,.25,.5,.75,1))
```


The Average from the women is 30.6 seconds and the average for men is 24.1 seconds. Men averaged going up and down the staris about 6.5 seconds faster.


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


We will run a t-test to test this hypothesis.

$H_0$ The average speed of the two genders are the same.
$H_a$ The average speed of the two genders are different.

```{r}
t.test(time_down_up~Gender, alternative='two.sided', 
  conf.level=.95, var.equal=FALSE, data=alldat)
```

```{r}
a <- na.omit(alldat$time_down_up[ which(alldat$Gender=='F')])
b <- na.omit(alldat$time_down_up[ which(alldat$Gender=='M')])
bs=bootstrp(a,b,1000)
```



Interprerting the results, we say that under the conditions that the null hypothesis is true the tests say we would see results like this 1 in 100 times.  I choose to reject the null hypothesis based on the low p-value.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
Our tests show that the men have faster times up and down the stairs than the women.