---
title: "Class Survey"
author: "Samantha Lee"
date: "October 8, 2018"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
  
We start by loading the data into 2 data frames.

```{r}
library(readr)
Sec02 <- read_csv("Class_Survey_Sec02.csv")
Sec23 <- read_csv("Class_Survey_Sec23.csv")
Sec02 <- mutate(Sec02,sect="PM")
Sec23 <- mutate(Sec23,sect="Eve")
alldat <- bind_rows(Sec02,Sec23)
```

```{r}
write.csv(x=alldat,file="alldat.csv")
```




#Questions to Answer
### 1)Is there a difference in average age between the two classes.
### 2)Is there a difference in breathold times between the guys and gals.
### 3)Is there a difference between time going up and down the stairs between guys and gals



# Question 1



# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->




#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


Here is a box plot of the ages of the evening and pm class.

```{r}
Boxplot(Age_yrs~sect, data=alldat, id=list(method="y"))
```


Looking at the graph, there appears to be approximately a 3-5 year age difference between the evening and the pm class; with the evening class having the older students.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

Here are the numerical summaries of the two classes ages.

```{r}
numSummary(alldat[,"Age_yrs", drop=FALSE], 
  groups=alldat$sect, statistics=c("mean", "sd", "IQR", 
  "quantiles"), quantiles=c(0,.25,.5,.75,1))
```


The Average from the evening class is 24.1 years old, and the average from the pm class is 19.9 years old.
According to the numerical summary, there is a 4.2 year age difference.


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


We will run a t-test to test this hypothesis.

$H_0$ The average age in the two classes are the same.  
$H_a$ The average age in the two classes are different.

```{r}
t.test(Age_yrs~sect, alternative='two.sided', 
  conf.level=.95, var.equal=FALSE, data=alldat)
```


Interprerting the results, we say that under the conditions that the null hypothesis is true the tests say we would see results like this 9 out of 1000 times.  I choose to reject the null hypothesis based on the low p-value.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Our tests show that the evening class has older students than the pm class.




#Question 2

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

First we create a box plot of the two breatholds
```{r}
Boxplot(Breathold~Gender, data=alldat, id=list(method="y"), xlab="Gender", 
  ylab="Breathold", main="Breathold 1")
```


```{r}
Boxplot(Breathold2~Gender, data=alldat, id=list(method="y"), xlab="Gender", 
  ylab="Breathold", main="Breathold 2")
```

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

Next we create summaries of the breatholds
```{r}
numSummary(alldat[,"Breathold", drop=FALSE], groups=alldat$Gender, 
  statistics=c("mean", "sd", "IQR", "quantiles"), quantiles=c(0,.25,.5,.75,1))
```

```{r}
numSummary(alldat[,"Breathold2", drop=FALSE], groups=alldat$Gender, 
  statistics=c("mean", "sd", "IQR", "quantiles"), quantiles=c(0,.25,.5,.75,1))
```





## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

We will run a t-test on both breatholds to test the hypothesis
$H_0$ The breathold speed of the two genders are the same.
$H_a$ The breathold of the two genders are different.

```{r}
t.test(Breathold~Gender, alternative='two.sided', 
  conf.level=.95, var.equal=FALSE, data=alldat)
```



```{r}
t.test(Breathold2~Gender, alternative='two.sided', 
  conf.level=.95, var.equal=FALSE, data=alldat)
```

Besed on the low p-values of both tests I choose to reject the null hypothesis.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Based on the evidence, guys had greater breathold times then gals.





# Question 3

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->


Are there differences between time up and down the stairs between guys and gals?


#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


Here is a box plot of the times going up and down the stairs of women and men.

```{r}
Boxplot(time_down_up~Gender, data=alldat, id=list(method="y"))
```


Looking at the graphical evidence, it appears the men went up and down the stairs about 5 seconds faster than the women.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

Here are the numerical summaries of the men and women's times.

```{r}
numSummary(alldat[,"time_down_up", drop=FALSE], 
  groups=alldat$Gender, statistics=c("mean", "sd", "IQR", 
  "quantiles"), quantiles=c(0,.25,.5,.75,1))
```


The Average from the women is 30.6 seconds and the average for men is 24.1 seconds. Men averaged going up and down the staris about 6.5 seconds faster.


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


We will run a t-test to test this hypothesis.

$H_0$ The average speed of the two genders are the same.
$H_a$ The average speed of the two genders are different.

```{r}
t.test(time_down_up~Gender, alternative='two.sided', 
  conf.level=.95, var.equal=FALSE, data=alldat)
```




Interprerting the results, we say that under the conditions that the null hypothesis is true the tests say we would see results like this 1 in 100 times.  I choose to reject the null hypothesis based on the low p-value.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
Our tests show that the men have faster times up and down the stairs than the women.
